Final Model Analysis

### 2017-08-27 model fitting/final_model.Rmd
fixed get_survival function

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
x <- as.data.frame(oshitar::setup())
library(survival); library(dplyr); library(rms)
```

@@

##### Validation with rms::validate for Somers’ Dxy rank correlation between pre-dicted log hazard and observed survival time, + slope shrinkage

@@

validation <- rms::validate(valmodel, method = "crossvalidation", B = 100, bw = F, dxy = TRUE, u = 0.5)
validation

@@

```{r}
# input vector of times to predict on + data set to be used in predictions
# function runs really slowly because it has to set up the data + fit the model everytime 
# outputs matrix of predicted survival 
# also include some kind of performance metric? measure of how accurately its predicting 
# sets up variables needed in the new data 
get_survival <- function(times, data) {
  newdata <- oshitar::variable_setup(data)
  x <- oshitar::setup()
  model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE)
  surv_probs <- pec::predictSurvProb(model, newdata = newdata, times)
  return(surv_probs)
}

get_survival(times = c(0.5, 1, 10), data = out)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
x <- oshitar::setup()
library(survival); library(dplyr); library(rms)
```

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(system.file("extdata/answers_data.csv", package = "oshitar"))

finaldata <- oshitar::variable_setup(out)
identical(finaldata$contain_answered, x$contain_answered)

write.csv(finaldata, file = "final_data.csv")
```

@@

##### Validation with rms::validate for Somers’ Dxy rank correlation between predicted log hazard and observed survival time + slope shrinkage

@@

validation <- rms::validate(valmodel, method = "crossvalidation", B = 100, bw = F, dxy = TRUE, u = 0.5)
validation
```

@@

```{r}
# input vector of times to predict on + data set to be used in predictions
# function runs really slow
# outputs matrix of predicted survival probabilities 
# also include some kind of performance metric? measure of how accurately its predicting 
# sets up variables needed in the new data 
get_survival <- function(times, data) {
  # setting up necessary variables in new data 
  newdata <- oshitar::variable_setup(data)

  # imports data to build model on 
  x <- read.csv("final_data.csv", head = TRUE)
  # builds model 
  model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE)
  # gets survival probabilities 
  surv_probs <- pec::predictSurvProb(model, newdata = newdata, times)
  return(surv_probs)
}
